---
title: "Assignment 2"
---

# Assignment 2

## 1. URLs

Filtered in imdb.com

<https://m.imdb.com/search/title/?title_type=feature&num_votes=2500,&country_of_origin=TR>

movies_2010_2023 \<- 2010-2023: <https://m.imdb.com/search/title/?title_type=feature&release_date=2010-01-01,2023-12-30&num_votes=2500,&country_of_origin=TR&count=250>

movies_before_2010 \<- - 2009: <https://m.imdb.com/search/title/?title_type=feature&release_date=,2009-12-31&num_votes=2500,&country_of_origin=TR&count=250>

Urls in vector

```{r}
#| echo: true
#| message: false
#| warning: false
movies_2010_2023 <- "https://m.imdb.com/search/title/?title_type=feature&release_date=2010-01-01,2023-12-30&num_votes=2500,&country_of_origin=TR&count=250"

movies_before_2010 <- "https://m.imdb.com/search/title/?title_type=feature&release_date=,2009-12-31&num_votes=2500,&country_of_origin=TR&count=250"

urls <- c(movies_2010_2023, movies_before_2010)

print(urls)
```

## 2. Web Scrapping

The libraries we will need are:

```{r}
#| echo: true
#| message: false
#| warning: false

library(tidyverse)
library(rvest)
library(stringr)
library(stringi)


```

Some functions I need:

```{r}
#| echo: true
#| message: false
#| warning: false
# GPT helped me that for functions.
# Prompt: Turkish characters cause some trouble how can we fix that?
# Function: convert Turkish characters to simple ASCII characters
simplify_text <- function(text) {
  # Geçersiz karakterleri kaldır ve UTF-8 kodlamasına zorla
  text <- iconv(text, from = "UTF-8", to = "ASCII//TRANSLIT", sub = "")
  
  # Başındaki ve sonundaki boşlukları temizle
  text <- gsub("^\\s+|\\s+$", "", text)
  
  return(text)
}

```

```{r}
#| echo: true
#| message: false
#| warning: false
# Function: Convert hours to minutes
convert_duration_to_minutes <- function(duration) {
  # Saat ve dakika formatını kontrol et
  if (grepl("^\\d+h$", duration)) {
    # If just hours (no minutes) (ex: "2h")
    hours <- as.numeric(gsub("h$", "", duration))
    return(hours * 60)
  } else {
    # Both (ex: "2h 7m")
    matches <- str_match(duration, "(\\d+)h (\\d+)m")
    hours <- as.numeric(matches[, 2])
    minutes <- as.numeric(matches[, 3])
    return(hours * 60 + minutes)
  }
}

```

```{r}
#| echo: true
#| message: false
#| warning: false

# Function: Clean the vote data
clean_vote <- function(vote) {
  # Remove double quotes and spaces.
  vote <- str_replace_all(vote, '"', "")         
  vote <- str_trim(vote) 
  
  # If it contains the letter 'K' (for thousands)
  if (grepl("K", vote)) {
    vote <- str_replace_all(vote, "[()K]", "")  
    vote <- str_replace_all(vote, "\\.", "")  
    return(as.numeric(vote) * 1000)             
  
    # If it contains the letter 'M' (for millions)
  } else if (grepl("M", vote)) {
    vote <- str_replace_all(vote, "[()M]", "")  
    return(as.numeric(vote) * 1e6)              
    
  # Others
  } else {
    vote <- str_replace_all(vote, "[()]", "")   
    return(as.numeric(vote))                  
  }
}

```

```{r}
#| echo: true
#| warning: false
# Create an empty list for all data
all_movies <- list()
all_cleaned_titles <- c()
all_years <- c()
all_durations <- c()
all_votes <- c()
all_ratings <- c()

for (url in urls) {
  data_html <- read_html(url)
  
# Pulling and cleaning headers
titles <- data_html |> 
  html_nodes('.ipc-title__text') |> 
  html_text() |> 
  tail(-1) |>
  head(-1)




# Fix encoding and spaces
cleaned_titles <- sapply(titles, simplify_text)

# Selecting unique titles and cleaning broken ones
cleaned_titles <- unique(cleaned_titles)  
cleaned_titles <- cleaned_titles[!grepl("\\?\\u", cleaned_titles)]

# Add to list
  all_cleaned_titles <- c(all_cleaned_titles, cleaned_titles)

# Pulling the years
  years <- data_html |> 
    html_nodes('.sc-300a8231-7.eaXxft.dli-title-metadata-item:nth-child(1)') |> 
    html_text() |> 
    str_extract("\\d{4}") |> 
    as.numeric()
  
  all_years <- c(all_years, years)
  
# Pulling the durations 
durations <- data_html |> 
  html_nodes('.sc-300a8231-7.eaXxft.dli-title-metadata-item:nth-child(2)') |> 
  html_text()


# Convert all times to minutes
durations_in_minutes <- sapply(durations, convert_duration_to_minutes)

# Add in List
 all_durations <- c(all_durations, durations_in_minutes)
  
# Pulling the ratings
  ratings <- data_html |> 
    html_nodes('.ipc-rating-star--rating') |> 
    html_text() |> 
    as.numeric()
  
  all_ratings <- c(all_ratings, ratings)
  
# Pulling and clearing the vote count
  votes_raw <- data_html |> 
    html_nodes('.ipc-rating-star--voteCount') |> 
    html_text()
  
  votes_clean <- sapply(votes_raw, clean_vote)
  
  all_votes <- c(all_votes, votes_clean)
  
  
  # Create data frame
  movies <- data.frame(
    Title = all_cleaned_titles,
    Year = all_years,
    Duration = all_durations,
    Rating = all_ratings,
    Votes = all_votes
  )
  
}

# Combine results
final_movies <- bind_rows(movies)

# Remove sequence number and dot
final_movies$Title <- gsub("^\\d+\\.\\s*", "", final_movies$Title)

# Remove unnecessary spaces
final_movies$Title <- trimws(final_movies$Title)



# Remove unnecessary spaces
print(final_movies)
```

## 3. Exploratory Data Analysis

### 3.a

```{r}
# Sort by IMDB rates
top_movies <- final_movies |> arrange(desc(Rating)) |> head(5)
bottom_movies <- final_movies |> arrange(Rating) |> head(5)

# View first 5 ve last 5 filmi
print(top_movies)
print(bottom_movies)

```

### 3.b

```{r}
# My favorite films
favorite_movies <- c("Yahsi Bati", "A.R.O.G", "G.O.R.A.")  # Örnek favoriler
favorite_movies_data <- final_movies |> filter(Title %in% favorite_movies)

print(favorite_movies_data)

```

### 3.c

We visualized the average IMDb scores and the number of movies by year.

```{r}
library(ggplot2)

# Average IMDb score by years
yearly_ratings <- final_movies |> 
  group_by(Year) |> 
  summarise(Average_Rating = mean(Rating, na.rm = TRUE), Movie_Count = n())

# Scatter plot
ggplot(yearly_ratings, aes(x = Year, y = Average_Rating)) +
  geom_point() +
  geom_line() +
  labs(title = "Yıllara Göre Ortalama IMDb Puanı", x = "Yıl", y = "Ortalama IMDb Puanı")

# Analysis of the number of films by years
ggplot(yearly_ratings, aes(x = Year, y = Movie_Count)) +
  geom_bar(stat = "identity") +
  labs(title = "Yıllara Göre Film Sayısı", x = "Yıl", y = "Film Sayısı")

```

### 3.d

Correlation between Votes and Ratings calculated.

```{r}
# Correlation analysis
correlation_votes_ratings <- cor(final_movies$Votes, final_movies$Rating, use = "complete.obs")
print(paste("Votes ve Ratings arasındaki korelasyon: ", correlation_votes_ratings))

# Scatter plot
ggplot(final_movies, aes(x = Votes, y = Rating)) +
  geom_point() +
  geom_smooth(method = "lm", col = "red") +
  labs(title = "IMDb Puanları ile Oy Sayısı Arasındaki İlişki", x = "Oy Sayısı", y = "IMDb Puanı")

```

### 3.e

The relationship between IMDb Scores and Movie Duration was examined.

```{r}
# Correlation analysis
correlation_duration_ratings <- cor(final_movies$Duration, final_movies$Rating, use = "complete.obs")
print(paste("Duration ve Ratings arasındaki korelasyon: ", correlation_duration_ratings))

# Scatter plot
ggplot(final_movies, aes(x = Duration, y = Rating)) +
  geom_point() +
  geom_smooth(method = "lm", col = "blue") +
  labs(title = "IMDb Puanları ile Film Suresi Arasındaki iliski", x = "Film Suresi (dakika)", y = "IMDb Puanı")

```

## 4. Top 1000

top1000_turkish_movies_url \<- https://www.imdb.com/search/title/?title_type=feature&groups=top_1000&country_of_origin=TR

```{r}
# URL for IMDb Top 1000 Turkish movies
imdb_top_1000_url <- "https://www.imdb.com/search/title/?title_type=feature&groups=top_1000&country_of_origin=TR"

# Pulling data from a web page
top_1000_html <- read_html(imdb_top_1000_url)

# Pull titles and years
top_1000_titles <- top_1000_html |> 
  html_nodes('.ipc-title__text') |> 
  html_text() |> 
  tail(-1) |>
  head(-1)

cleaned_top_titles <- sapply(top_1000_titles, simplify_text)

# Selecting unique titles and cleaning broken ones
cleaned_top_titles <- unique(cleaned_top_titles)
cleaned_top_titles <- cleaned_top_titles[!grepl("\\?\\u", cleaned_top_titles)]

top_1000_years <- top_1000_html |> 
  html_nodes('.sc-300a8231-7.eaXxft.dli-title-metadata-item:nth-child(1)') |> 
  html_text() |> 
  as.numeric()

# Create a new data frame
top_1000_df <- data.frame(Title = cleaned_top_titles, Year = top_1000_years)


# Remove sequence number and dot
top_1000_df$Title <- gsub("^\\d+\\.\\s*", "", top_1000_df$Title)

# Remove unnecessary spaces
top_1000_df$Title <- trimws(top_1000_df$Title)


# Check the result
print(top_1000_df)



```

```{r}
# Merge data sets
merged_df <- left_join(top_1000_df, final_movies, by = c("Title", "Year"))

# Check the result
print(merged_df)

```

```{r}
# Sort by IMDb score
ranked_movies <- merged_df |> arrange(desc(Rating))

# Check sequential data frame
print(ranked_movies)

# Check out the top 11 movies
head(ranked_movies, 11)

```

```{r}
# Average IMDb score
average_rating <- mean(ranked_movies$Rating, na.rm = TRUE)
print(paste("Top 1000 Türk Filmlerinin Ortalama IMDb Puanı: ", average_rating))

ggplot(ranked_movies, aes(x = Year)) +
  geom_density(fill = "lightblue", alpha = 0.7) +
  labs(
    title = "Top 1000 Türk Filmlerinin Yıllara Göre Yoğunluğu",
    x = "Yıl",
    y = "Yoğunluk"
  ) +
  theme_minimal()



```

Some movies were not in the top 1000, this is because IMDb filters itself by year and the movie made in 1975 does not appear.
